\documentclass[output=paper,
% modfonts,colorlinks,citecolor=brown,newtxmath
]{langscibook} 
% \bibliography{localbibliography}

% \input{localpackages.tex}
% \input{localcommands.tex}

%\usepackage{qtree}

% \usepackage{tikz}

% \usepackage{forest} 
\forestset{sn edges/.style={
for tree={
parent anchor=south, child anchor=north, 
calign=fixed edge angles, 
calign primary angle=-60, calign secondary angle=60, 
align=center, base=t},
delay={
where content={}{shape=coordinate,
for parent={for children={anchor=north}}}{}} 
}}
\forestset{
	roof/.style={edge path'={%
	(.parent first)--(!u.children)--(.parent last)--cycle
	}
	},
	}
	
\title{How to introduce instrumental agents: Evidence from binding in Russian event nominal phrases} 

\author{%
 Takuya Miyauchi\affiliation{Tokyo University of Foreign Studies and\\Japan Society for the Promotion of Science}
}
 
\abstract{
The aim of this paper is to argue that instrumental agents in Russian are introduced by a silent P through binding phenomena by instrumental agents in event nominal phrases. Two assumptions are adopted in this paper: one is the absence of the DP layer in Russian based on binding phenomena and the other is a particular structure of event nominal phrases. I show that the appropriateness of proposing a silent P is supported by Generalized Case Realization Requirement in Russian and that the silent P is a lexical preposition, not a functional one due to its ability to bind objects out of PP.

\keywords{Russian, event nominal phrases, DP--NP, instrumental agents}
}

% \togglepaper[8]

\begin{document}%
\maketitle
\shorttitlerunninghead{How to introduce instrumental agents}

\section{Introduction}
In this paper, I claim that instrumental agents in Russian are introduced by a silent P (ø), through binding phenomena by instrumental agents in event nominal phrases. Two assumptions are adopted here: one is the structure of event nominal phrases proposed by \cite{MiyauchiIto2016, Miyauchi2017b}, and the other is that Russian nominal phrases are not DP but NP. I discuss that \textsc{Generalized Case Realization Requirement} (GCRR) in Serbo-Croatian \citep{Horvath2014} can apply (at least partially) to Russian and show that setting a silent P is appropriate via this discussion. Finally, I point out a possibility to bind objects out of PP and demonstrate that the silent P is a lexical preposition, not a functional one. 


The rest of this paper is organized as follows. In \sectref{sec:BIND}, I outline discussion on the structure of nominal phrases through  Russian binding phenomena. \sectref{sec:EVN} offers a syntactic account on a restriction of θ-roles of genitive nouns in event nominal phrases with some assumptions, based on \cite{MiyauchiIto2016, Miyauchi2017b}. In \sectref{sec:INS}, I propose the syntactic structure of event nominal phrases containing instrumental agents and \sectref{sec:GCRR} shows validity of GCRR in Russian. \sectref{sec:PP} points out that there are binding phenomena out of PP in Russian and the proposed structure is modified. Finally, \sectref{sec:CON} concludes the paper. 

\section{Russian binding phenomena and the structure of nominal phrases}\label{sec:BIND}

The structure of Slavic nominal phrases without overt articles is controversial in terms of whether they have DP in their structure or not. Some researchers insist on the presence of DP even in Slavic (\citealt{Progovac1998,Rappaport2002,Rutkowski2002,Basic2004,FranksPereltsvaig2004,Pereltsvaig2007a,RutokowskiMaliszewska2007,Laterza2016} etc.), while others maintain that nominal phrases in Slavic are NPs (\citealt{Zlatic1998,Trenkic2004,Boskovic2005, Boskovic2007, Boskovic2009,Petrovic2011,Despic2013} etc.).

In this paper, I investigate instrumental agents in event nominal phrases in Russian from the standpoint of the no-DP analysis.\footnote{Note that the NP/DP debate itself is beyond the scope of this paper. Please see the references cited above for arguments for and against the DP projection in Slavic.} 
In this section, I outline the discussion of the structure of nominal phrases through Russian binding phenomena, which gives support to the no-DP analysis, based on \citeposst{Despic2013} paradigm.\footnote{The content of this section is based on \citet{Miyauchi2016}. Please see \citet{Miyauchi2016} for more details.}  
\citet{Despic2013} argues that binding phenomena and \citeposst{Kayne1994} antisymmetry approach provide a key to examine the existence or absence of the DP projection. He concludes that there are is no DP in Serbo-Croatian and that the D-like elements are adjuncts. 

Following \citet{Despic2013}, I adopt \citeposst{Kayne1994} definition of c-command given in \REF{def}.\footnote{I use this definition of c-command henceforth.}

\begin{exe}
\ex\label{def}
X c-commands Y iff X and Y are categories, X excludes Y and every category that 	dominates X dominates Y.	
\hfill \citep[16]{Kayne1994}
\end{exe}

\noindent
The definition of exclusion is as follows \REF{exc}:

\begin{exe}
\ex\label{exc} α excludes β if no segment of α dominates β.
\hfill \citep[9]{Chomsky1986}
\end{exe}

\noindent
The Russian sentences \REF{binr}, \REF{binr2}, and \REF{binr3} are ungrammatical with co-reference between possessors and pronouns, while \REF{binrpos}, \REF{binrpos2}, and \REF{binrpos3} are grammatical. There is a clear contrast between \REF{binr}, \REF{binr2}, \REF{binr3} and \REF{binrpos}, \REF{binrpos2}, \REF{binrpos3}.

\begin{exe}\ex\label{bin}
\begin{xlist}
\ex[*]{ \label{binr}
\gll Kolin$_i$ poslednij fil'm sil'no ego$_i$ razočaroval. \\
	Kolya's latest film really him disappointed\\
\trans Intended: `Kolya$_i$'s latest film really disappointed him$_i$.'}
\ex[]{ \label{binrpos}
\gll Poslednij fil'm Koli$_i$ sil'no ego$_i$ razočaroval. \\
	latest film Kolya.{\GEN} really him disappointed\\
\trans `The latest film of Kolya$_i$ really disappointed him$_i$.'}
\end{xlist}
\end{exe}

\begin{exe}\ex\label{bind2}
\begin{xlist}
\ex[*]{ \label{binr2}
\gll Vanin$_i$ papugaj ukusil ego$_i$ včera.\\ 
     Vanya's parrot bit him yesterday\\ 
\trans Intended: `Vanya$_i$'s parrot bit him$_i$ yesterday.'}
\ex[]{ \label{binrpos2}
\gll Papugaj Vanin$_i$ ukusil ego$_i$ včera.\\ 
      parrot Vanya.{\GEN} bit him yesterday\\ 
\trans `The parrot of Vanya$_i$ bit him$_i$ yesterday.'}
%\trans `Vanya$_i$'s parrot bit him$_i$ yesterday.'
\end{xlist}
\end{exe}
\begin{exe}\ex\label{bind3}
\begin{xlist}
\ex[*]{ \label{binr3}
\gll Sašin$_i$  mjač včera udaril ego$_i$ po golove. \\
     Sasha's ball yesterday hit him in head\\
\trans Intended: `Sasha$_i$'s ball hit him$_i$ in the head yesterday.'}
\ex[]{ \label{binrpos3}
\gll Mjač Saši$_i$ včera udaril ego$_i$ po golove. \\
     ball Sasha.{\GEN} yesterday hit him in head\\
\trans `The ball of Sasha$_i$ hit him$_i$ in the head yesterday.'}
%\trans `Sasha$_i$'s ball hit him$_i$ in the head yesterday.'
\end{xlist}
\end{exe}

\noindent
Let us see \REF{bin} as a representative case. 
Following \citet{Despic2013}, I argue that \REF{binr} is ungrammatical because the possessor \textit{Kolin} `Kolya's' binds the co-indexed pronoun \textit{ego} 'him,' which results in Condition B violation. 
According to the reasoning in \citet{Despic2013}, this suggests that Russian nominal phrases lack the DP layer.\footnote{An anonymous reviewer argues that the Serbo-Croatian data in \citet{Despic2013} corresponding to the examples \REF{bin}--\REF{bind3} are not ungrammatical, which suggest \citeposst{Despic2013} conclusion about the presence/absence of the DP layer in Serbo-Croatian is questionable, but as I am only concerned with Russian here, I don't have much to add. I am only employing the reasoning and the structure of the argument developed in \cite{Despic2013}. My argument for the lack of DP in Russian is thus valid regardless of the quality of \citeposst{Despic2013} Serbo-Croatian data.} \figref{bindtreerus} shows the structure of \REF{binr}.\footnote{The object \textit{ego} `him' in  \REF{binr} is scrambled and the word order of this sentence becomes SOV. For the sake of simplicity, however, scrambling is ignored in the \figref{bindtreerus}. I take the basic word order in Russian to be SVO, following \citet{Isachenko1966}.}  
Note that under \citeposst{Kayne1994} theory, specifiers are taken to be adjoined phrases. Consequently, specifiers are not distinguished from adjuncts and the bar-level notation does not make sense.\footnote{I do not use the bar-level notation. The conventional X$'$ (X-bar/X-prime) is written as XP or is omitted in the trees in this paper.} 

\begin{figure}[h]
\caption{The structure of \REF{binr}}
\label{bindtreerus}
\begin{forest}
  sn edges [ CP [ C ] 
                [ TP$_1$ [ NP$_1$ [ Kolya$_i$'s ]
                                  [ NP$_2$ [ AP [ latest, roof] ] 
                                           [ N [film ] ] ] ]
                         [ TP$_2$ [ T ] 
                                  [ VP [ really ] 
                                       [ [ V [ disappointed ] ] 
                                         [ NP [ him$_i$, roof] ] ] ] ] ] ]
\end{forest}
\end{figure}

In \figref{bindtreerus}, the first category dominating `Kolya's' is CP, which also dominates the object NP `him.'\footnote{Note that NP$_1$ and TP$_1$ are segments not categories.} Therefore, the possessor `Kolya's' c-commands the object `him', violating Condition B.
Accordingly, \REF{binr} is ungrammatical.
If there was an additional DP layer in the nominal phrase, as illustrated in \figref{rusd}, the possessor `Kolya's' would not c-command the pronoun and there would thus be no Condition B violation. \REF{binr} should be grammatical, contrary to fact.

\begin{figure}[h]
\caption{The structure of the subject of \REF{binr} with a DP layer}
\label{rusd}
\begin{forest}
  sn edges [ DP [ D ] 
                [ NP$_1$ [ Kolya$_i$'s ] 
                         [ NP$_2$ [ AP [ latest, roof] ] 
                                  [ N [ film ] ] ] ] ]
\end{forest}
\end{figure}

In \figref{rusd}, `Kolya's' is dominated by the category DP, which does not dominate any other node outside of the nonimal phrase. That is to say, the possessor `Kolya's', does not c-command the object NP. For this reason, with the DP layer, there would be no violation of Condition B in sentences like \REF{binr} and these sentences should be grammatical. Thus, it is concluded that the ungrammaticality of \REF{binr} shows that there is no DP layer in Russian.

How can we capture the grammaticality of \REF{binrpos}?
Generally, the genitive possessor NP is supposed to be located in the complement of the (head) NP (\citealt[38]{Franks1995}; \citealt[214]{Bailyn2012}; \citealt[84]{Mitrenina2012}).\footnote{To be precise, \citet{Bailyn2012} does not propose this structure.	According to \citet{Bailyn2012}, adnominal genitives occupy the complement of QP in \REF{fni}:

			\ea\label{fni}
			\relax[$_\textrm{NP}$ N [$_\textrm{QP}$ Q [\textsubscript{NP\textsubscript{\textsc{gen}}}\ \ ] ] ]
			\hfill (\citealt[214]{Bailyn2012}; slightly modified by the author)
			\z

			\noindent
			\citet[214]{Bailyn2012} proposes that Q assigns the genitive case to the sister NP (there is a case where Q is covert). However, these differences in the positions of genitive NP	have no effect on the argument of this paper since genitive possessor NP is located lower than possessee NP.}
\figref{bindtreeGEN} represents the structure of \REF{binrpos}.

\begin{figure}[h]
\caption{The structure of \REF{binrpos}}
\label{bindtreeGEN}
\begin{forest}
  sn edges [ CP [ C ] 
                [ TP$_1$ [ NP$_1$ [ AP [ latest, roof] ] 
                                  [ NP$_2$ [ N [film ] ] 
                                           [ NP\textsubscript{\textsc{gen}} [ Kolya.\textsc{gen}$_i$, roof] ] ] ] 
                         [ TP$_2$ [ T ] 
                                  [ VP [ really ] 
                                       [ [ V [ disappointed ] ] 
                                         [ NP [ him$_i$, roof] ] ] ] ] 
                ] ]
\end{forest}
\end{figure}


In this case, the categories dominating NP$_{\textsc{gen}}$ are NP$_1$ and CP. NP$_{\textsc{gen}}$ does not c-command the object NP because the subject NP$_1$ does not dominate the object NP. Thus, there is no Condition B violation and sentences like \REF{binrpos} are grammatical.

The contrast in grammaticality between prenominal possessive constructions \REF{binr}, \REF{binr2}, \REF{binr3} and postnominal ones \REF{binrpos}, \REF{binrpos2}, \REF{binrpos3} supports the argument that the DP is not projected in Russian.
For the rest of the paper, I adopt the no-DP analysis of Russian nominal phrases.


\section[Russian event nominal phrases and their structures]{Russian event nominal phrases and their structures\label{sec:EVN}\protect\footnote{The content of this section is mostly based on \cite{MiyauchiIto2016, Miyauchi2017b}. Please see \cite{MiyauchiIto2016, Miyauchi2017b} for more details.}} 

\subsection{Russian event nominals}

An ``event nominal'' denotes an event or process and inherits argument structure of its base verb (\citealt{Grimshaw1990} in general, \citealt{Schoorlemmer1998}, \citealt{Pazelskaya2007} for Russian). 
It can be followed by a genitive complement in Russian.

\begin{exe}\ex \label{type}%Three types of event nominals
\begin{xlist}
\ex \label{type1}
\textit{Type 1:} \ding{51} external argument / \ding{55}\ internal argument\\\samepage
%%$^{\checkmark}${ext}.arg. / *{int}.arg. → Type1
\gll	udar \minsp{\{} {mužčiny} / \minsp{*} {stola}\}\\
		hit {} man.{\GEN} {} {} table.{\GEN}\\
\trans `the hit of \{the man / the table\}'

\ex \label{type2}
\textit{Type 2:} \ding{51} external argument / \ding{51} internal argument\\
\gll	ispolnenie \minsp{\{} {Šaljapina} / {arii}\}\\
		performance {} Chaliapin.{\GEN} {} aria.{\GEN}\\
\trans `the performanc of \{Chaliapin / the aria\}'\samepage

%\newpage
\ex \label{type3}
\textit{Type 3:} \ding{55}\ external argument / \ding{51} internal argument\\
\gll	razrušenie \minsp{\{*} {vraga} / {goroda}\}\\
		destruction {} enemy.{\GEN} {} city.{\GEN}\\
\trans `the destruction of \{the enemy / the city\}'
\end{xlist}
\end{exe}

\noindent This kind of restriction of genitive complements' θ-roles  is thought to result from argument structures of event nominals \citep{Pazelskaya2007}.
Therefore these phenomena have been dealt with as lexical problems.
\cite{MiyauchiIto2016, Miyauchi2017b} tried to provide more principled explanation for these phenomena as syntactic problems based on phase theory.

I adopt the framework of \textsc{Distributed Morphology} \citep{HalleMarantz1993}, in which $\surd$ (root) moves to a categorizer (\textit{n, v, a} etc.) to determine its category.
The contention of \cite{MiyauchiIto2016, Miyauchi2017b} is that type 1 nominals and type 2/3 nominals differ structurally.
I adopt the structure in \figref{type23tr} for all event nominals and explain below how the two types differ.

\begin{figure}[H]
\caption{The structure of the event nominal phrases}
\label{type23tr}
\begin{forest}
  sn edges [ (VoiceP) [ (Voice) [ -\textit{nie}/-\textit{tie} ] ] 
                      [ XP [ X ]
                           [ \textit{n}P [ \textit{n} ] 
                                       [ $\surd$P [ $\surd$ ] 
                                                  [ (\textsc{int-arg}) ] ] ] ] ]
\end{forest}
\end{figure}

\noindent 
Unlike in type 2/3, which project the entire structure, VoiceP is not projected in type 1. 
This structural difference is supported by 
the absence of a verbal nominalizer \textit{-nie/-tie} in type 1 nominals.\footnote{This argument assumes that the nominalizer occupies the head of VoiceP. Support for this assumption comes from the fact that the nominalizer is morphologically complex and seems to include the passive participle morpheme \textit{-n-/-t-} \citep{Babby1997}.} 
I suppose that $\surd$ directly takes an internal argument following \citet{Harley2009a}.
Moreover, a functional head, X, licenses genitive Case through Agree.\footnote{This X is a counterpart of Num(ber) in \citet{Carstens2001}, which is claimed to be a licenser of Case. \citet{Bailyn2012}, on the other hand, argues that the genitive case assigner in Russian is Q. The true identity of X lies outside the scope of this paper.} 

I assume \citeposst{Chomsky2000} phase theory and the proposal that \textit{n}P is a phase (\citealt{Carstens2001, Arad2003, Hicks2009} etc.). It then follows from \textsc{Phase Impenetrability Condition}, shown in \REF{PIC}, that internal arguments cannot be genitive in type 1 nominals.


\begin{exe}
\ex\label{PIC} \textit{Phase Impenetrability Condition (PIC)}\\
In phase α with head H, the domain of H is not accessible to 
operations outside α, only H and its edge are accessible to such operations.\\
%{} \hfill \citep[108]{Chomsky2000}
\end{exe}
\vspace{-2em}
\hfill \citep[108]{Chomsky2000}
\vspace{1em}

\noindent In type 2/3 nominals, the head of $\surd$P moves to the nominalizer \textit{-nie/-tie}, the head of VoiceP, in order to derive its form. 
Therefore, the \textit{n}P phase slides up to VoiceP due to \textsc{phase-sliding} \citep{Gallego2010}.\footnote{According to phase-sliding, when a verb head-moves from \textit{v}$^*$ to T, the phasehood of \textit{v}$^*$ also moves to T. I can generalize this proposal: when X, a phase, head-moves to Y,  the phasehood of X also moves to Y. Thus, phase-sliding can be applied to event nominals. In this example, $\surd$ moves to VoiceP stopping at \textit{n} and X, picking them up along the way because of the head movement constraint \citep{Travis1984, Matushansky2006}. Since \textit{n} is a phase head, phase-sliding also occurs.} The size of the new phase is shown with a box in \figref{type23trre}.

\begin{figure}[h]
\caption{The structure of event nominal phrases with phase-sliding}
\label{type23trre} 
%\Tree [.VoiceP [.Voice {-\textit{nie} / -\textit{tie}} ] [.XP [.X ] [.\textit{n}P [.\textit{n} ] [.$\surd$P [.$\surd$ ] \textsc{int-arg} ] ] ]!{\qframesubtree} ]
%[_{DP} D [_{VoiceP} \fbox{[_{XP} [_{nP} [_{\surd P} Patient $\surd$ ] \textit{n} ] X ] Voice ] ]}
\begin{forest}
  sn edges [ VoiceP [ Voice [ -\textit{nie}/-\textit{tie} ] ] 
                    [ XP, tikz={\node [draw,fit to=tree]{};}
                         [ X ]
                         [ \textit{n}P [ \textit{n} ] 
                                     [ $\surd$P [ $\surd$ ] 
                                                [ (\textsc{int-arg}) ] ] ] ] ]
\end{forest}
\end{figure}

Thus, phase-sliding makes it possible that X Agrees with an internal argument, not violating PIC. Consequently, internal arguments are allowed to have genitive Case. 


\subsection{Genitive external arguments}

To avoid wrong prediction, I suppose two external θ-roles: possessor (\textsc{Poss}) and agent (\textsc{Ag}).
In type 1/2, \textsc{Poss} is merged in the specifier of \textit{n}P (\citealt{Carstens2000, Carstens2001, Adger2003} etc.). 
By contrast, \textsc{Ag} in the type 3 is adjoined to VoiceP like \textit{by} phrases in English \citep{Bruening2013}.\footnote{In fact, a distinction between specifiers and adjuncts cannot be made under \citeposst{Kayne1994} theory. What is significant here, however, is the structural difference between \textsc{Poss} and \textsc{Ag}. That is, \textsc{Poss} is located in the \textit{n}P domain, while \textsc{Ag} is in the VoiceP domain.}
\textsc{Poss} is c-commanded by the probe, X and thus
X can Agree with it as illustrated in \figref{external}.
Consequently, external arguments in type 1/2 can be genitive at the postnominal position.
On the other hand, \textsc{Ag} is not c-commanded by the probe X  and hence X cannot Agree with it as schematized in \figref{external}.
This is why external arguments in type 3 cannot appear in genitive case postnominally.\footnote{In addition to these structures of event nominal phrases, 
			\citet{Miyauchi2017b} suggests
			that there are two types on \textit{n}P through semantic analyses. Please see \citet[section 5]{Miyauchi2017b} for more details.}

\begin{figure}[h]
\caption{The structure of event nominal phrases with external θ-roles}
\label{external}
%\Tree [.{(VoiceP)} [ [.{(Voice)} {-\textit{nie}/-\textit{tie}} ] [.XP [.X ] [.\textit{n}P [ [.\textit{n} ]!\qsetw{.5in} \qroof{{\ \ \ }$\surd${\ \ \ }}.$\surd$P ]!\qsetw{1in} \textsc{Poss} ]!\qsetw{1in} ] ]!\qsetw{1.5in} \textsc{Ag} ]
%[.{(VoiceP)} [ [.{(Voice)} {-\textit{nie}/-\textit{tie}} ] [.XP [.X ] [.\textit{n}P [ [.\textit{n} ] [.$\surd$P [.$\surd$ ]!\qsetw{0.5in} {(\textsc{int-arg})} ] ]!\qsetw{1in} \textsc{Poss} ]!\qsetw{1in} ] ]!\qsetw{1.5in} \textsc{Ag} ]
\begin{forest}
  sn edges [ (VoiceP) [ [ (Voice) [ -\textit{nie}/-\textit{tie} ] ] 
                        [ XP [ X ]
                             [ \textit{n}P [ [ \textit{n} ] 
                                           [ $\surd$P [ {\ \ $\surd$\ \ }, roof] ] ] 
                                         [ \textsc{Poss} ] ] ] ]
                       [ \textsc{Ag} ]  ]
\end{forest}
\end{figure}

\section{Instrumental agents introduced by silent P}\label{sec:INS}

\subsection{Russian event nominals with instrumental agents}


Double genitives are basically banned in Russian as shown in examples \REF{ispGG}, \REF{razGG}, where type 2 and type 3 nominals are used.
When both internal and external arguments are expressed in the same phrase, the former is assigned the genitive case and the latter is assigned the instrumental case as indicated in \REF{ispGI}, \REF{razGI}.

\begin{exe}
\ex\label{ispG} \textit{Type 2}
\begin{xlist}
\ex[*]{\label{ispGG}
\gll ispolnenie arii Šaljapina\\
	performance aria.{\GEN} Chaliapin.{\GEN}\\
\trans Intended: `the performance of aria by Chaliapin'} \hfill\citep[162]{Ljutikova2016}
\ex[]{\label{ispGI}
\gll ispolnenie arii Šaljapinym\\
	performance aria.{\GEN} Chaliapin.{\INS}\\
\trans `the performance of aria by Chaliapin' \hfill\citep[64]{Gerasimova2016}}
\end{xlist}
\end{exe}

\begin{exe}
\ex\label{razG} \textit{Type 3}
\begin{xlist}
\ex[*]{\label{razGG}
\gll razrušenie goroda vraga\\
	destruction city.{\GEN} enemy.{\GEN}\\
\trans Intended: `the destruction of the city by the enemy' }

%\newpage
\ex[]{\label{razGI}
\gll razrušenie goroda vragom\\
	destruction city.{\GEN} enemy.{\INS}\\\samepage
\trans `the destruction of the city by the enemy' }
\end{xlist}
\end{exe}

\noindent In Serbo-Croatian, if the agent nominal is a complex phrase, the double genitive construction is perfectly acceptable as shown in \REF{dgsc}.\footnote{
			This was kindly pointed out by an anonymous reviewer.}

\begin{exe}
\ex\label{dgsc} %Serbo-Croatian\vspace{-1ex}
\gll snimak požara Emira Kusturice\\
	record fire.{\GEN} Emir.{\GEN} Kusturica.{\GEN}\\
\trans `the shot of the fire by Emir Kustiruca'
\end{exe}

\noindent
However, in Russian, even if agents are complex, double genitives are not permitted as indicated in \REF{dgr}.\footnote{
			Although the micro-variation between Serbo-Croatian \REF{dgsc} and Russian \REF{dgr} is significant, this paper cannot address this contrast since it focuses on only Russian.}

\begin{exe}
\ex\label{dgr} %Russian\samepage
\begin{xlist}
\ex[*]{
\gll s'emka požara Ivana Andreeviča\\
	shot fire.{\GEN}	Ivan.{\GEN} Andreevich.{\GEN}\\
\trans Intended: `the shot of fire by Ivan Andreevich'}
\ex[*]{
\gll ispolnenie arii izvestnogo	 pevca Šaljapina\\
	performance aria.{\GEN} famous.{\GEN} singer.{\GEN} Chaliapin.{\GEN}\\
\trans Intended: `the performance of aria by the famous singer, Chaliapin' }
\end{xlist}
\end{exe}

\noindent
Of course, as is the case with \REF{ispG}, \REF{razG}, the phrases are acceptable when the complex agents are instrumental as show in \REF{gicom}.

\begin{exe}
\ex\label{gicom} %Russian
\begin{xlist}
\ex
\gll s'emka požara Ivanom Andreevičem\\
	shot fire.{\GEN}	Ivan.{\INS} Andreevich.{\INS}\\
\trans  `the shot of fire by Ivan Andreevich' 
\ex
\gll ispolnenie arii izvestnym	 pevcom Šaljapinym\\
	performance aria.{\GEN} famous.{\INS} singer.{\INS} Chaliapin.{\INS}\\
\trans `the performance of aria by the famous singer, Chaliapin' 
\end{xlist}
\end{exe}

\noindent Instrumental phrases can appear as agents of \textsc{complex event nominals} (CEN), which have argument structures.  
CEN obligatorily take internal arguments and overtly express them (\citealt{Revzin1973, Schoorlemmer1998} etc.). 
That is, an instrumental agent cannot appear without an internal argument unless it is elided as illustrated in \REF{II}--\REF{DI}.\footnote{
			$\Delta$ in \REF{DI} expresses a deleted internal argument.			}

\begin{exe}
\ex\label{II}
\begin{xlist}
\ex[*]{\label{ispI}
\gll ispolnenie Šaljapinym\\
	performance Chaliapin.{\INS}\\
\trans Intended: `the performance by Chaliapin' \hfill\citep[90]{Revzin1973}}
\ex[*]{\label{razI}
\gll razrušenie vragom\\
	destruction enemy.{\INS}\\
\trans Intended: `the destruction by the enemy' }
\end{xlist}
\end{exe}

\begin{exe}
\ex\label{DI}
\begin{xlist}
\ex\label{ispdI}
\gll ispolnenie $\Delta$ Šaljapinym \\  %%$\partial$
	performance {} Chaliapin.{\INS}\\
\trans `the performance by Chaliapin of ...'

\ex\label{razdI}
\gll razrušenie $\Delta$ vragom\\
	destruction {} enemy.{\INS}\\
\trans `the destruction by the enemy of ...' 
\end{xlist}
\end{exe}

\noindent
The type 2 and 3 nominals have VoiceP as mentioned in \sectref{sec:EVN}. 
If I assume that instrumental agentive phrases are located at a domain related with VoiceP, it is natural that the type 1 nominals cannot have  instrumental agentive phrases because of the absence of VoiceP.
This is reflected in the ungrammaticality of \REF{ud}.

\begin{exe}
\ex\label{ud} \textit{Type 1}
\begin{xlist}
\ex[*]{\label{udGI}
\gll	udar {stola} mužčinoj\\
		hit table.{\GEN} man.{\INS}\\
\trans Intended: `the hit the table by the man'}

\ex[*]{\label{udI}
\gll udar mužčinoj\\
	hit man.{\INS}\\
\trans Intended: `the hit by the man'}
\end{xlist}
\end{exe}


\subsection{Binding in Russian event nominals and instrumental agents as VoiceP specifiers/adjuncts}

Contrast in binding similar to the one presented in \REF{bin}--\REF{bind3} is observed also with instrumental agents in event nominal phrases, as shown in \REF{binins} and \REF{binins2}.\footnote{
			An anonymous reviewer pointed out that in Serbo-Croatian the postnominal doubled genitive can co-refer a personal pronoun as shown in \REF{fnii} below. 

\ea[]{\label{fnii}
\gll Snimak požara \minsp{[} Emira Kusturice]$_i$ napravio je od njega$_i$ reportersku zvezdu.\\ 
      record fire.{\GEN} {} Emir.{\GEN} Kusturica.{\GEN} made {\AUX} from him reporter star\\ 
\glt `The shot of the fire by [Emir Kusturica]$_i$ made him$_i$  star reporter.'}
\z

            \noindent Unlike Serbo-Croatian, Russian bans doubled genitives as indicated in \REF{dgr}, so I have nothing further to say on this topic.}

\begin{exe}
\ex\label{binins}
\begin{xlist}
\ex[*]{\label{contPOSS}
\gll  {Ivanovo}$_i$  narušenie  {pravil}  ogorčaet  ego$_i$.\\
	Ivan's violation rules.{\GEN} distresses him\\
\trans Intended: `Ivan$_i$'s violation of the rules distresses him$_i$.'}
\ex[]{\label{contINS}
\gll  Narušenie  {pravil}  {Ivanom}$_i$  ogorčaet  ego$_i$.\\
%	violation rule.{\GEN} I.{\INS} distresses him\\
	violation rules.{\GEN} Ivan.{\INS} distresses him\\
\trans `The violation of the rules by Ivan$_i$ distresses him$_i$.'}
\end{xlist}
\end{exe}

\begin{exe}
\ex\label{binins2}
\begin{xlist}
\ex[*]{\label{contPOSS2}
\gll Ivanovo$_i$  ubijstvo  Viti gluboko opečalilo ego$_i$.\\
	Ivan's murder Vitya.{\GEN} deeply saddened him\\
\trans Intended: `Ivan$_i$'s murder of Vitya deeply saddened him$_i$.'}
%	{} Ivan's murder Vitya-GEN distresses him\\
%\trans `The Ivan$_i$'s murder of Vitya distresses him$_i$'
\ex[]{\label{contINS2}
\gll  Ubijstvo  Viti  Ivanom$_i$ gluboko opečalilo ego$_i$.\\
	murder Vitya.{\GEN} Ivan.{\INS} deeply saddened him\\
\trans `The murder of Vitya by Ivan$_i$ deeply saddened him$_i$.'}
%\gll  Ubijstvo  Viti$_i$  Ivanom_j  ogorčaet  ego_{i/j}.\\
%	murder Vitya-GEN Ivan-INS distresses him\\
%\trans `The murder of Vitya by Ivan$_i$ distresses him$_i$'
\end{xlist}
\end{exe}

\noindent
\REF{contPOSS}, \REF{contPOSS2} are ungrammatical, while \REF{contINS}, \REF{contINS2} are grammatical.

Applying the structure of event nominals in \figref{external} to \REF{contPOSS} and \REF{contINS}, the structure of \REF{contPOSS} and \REF{contINS} is illustrated in \figref{bindtreePOSS} and \figref{bindtreeINS}.
%\footnote{
%			Note that in \figref{bindtreeINS}, the nodes below XP$_2$ are omitted as they repeat the structure in \figref{bindtreePOSS}. }
I assume that the instrumental agents are specifiers/adjuncts to VoiceP as the genitive external arguments in type 3 nominals.\footnote{This position can explain the fact that type 1 event nominals cannot have instrumental agents as shown in \REF{ud}.} 


\begin{figure}[h]
\caption{The structure of \REF{contPOSS}}
\label{bindtreePOSS}
\begin{forest}
  sn edges [ VoiceP$_1$ [ Ivan$_i$'s ]
                        [ VoiceP$_2$ [ Voice [ violation ] ] 
                                     [ XP [ X ]
                                          [ \textit{n}P [ \textit{n} ] 
                                                      [ $\surd$P [ $\surd$ ] 
                                                                 [ rules.{\GEN} ] ] ] ] ] ]
\end{forest}
\end{figure}

\begin{figure}[h]
\caption{The structure of \REF{contINS}}
\label{bindtreeINS}
%\Tree [.VoiceP$_1$ [.VoiceP$_2$ [.Voice narušenie ] [.XP [.X  ] [.\textit{n}P \textit{n} [.$\surd$P [.$\surd$ ]!\qsetw{0.7in} {pravil} ] ] ] ]!\qsetw{1.2in} {Ivanom}$_i$ ] 
\begin{forest}
  sn edges [ VoiceP$_1$ [ VoiceP$_2$ [ Voice [ violation ] ] 
                                     %[ {XP\\{...}}
                                     [ XP [ X ]
                                          [ \textit{n}P [ \textit{n} ] 
                                                      [ $\surd$P [ $\surd$ ] 
                                                                 [ rules.{\GEN} ] ] ] 
                                     ] 
                         ] 
                        [ Ivan.{\INS}$_i$ ] ]
\end{forest}
\end{figure}



As mentioned above, \citet{Schoorlemmer1998} pointed out that only CEN can have the instrument agentive phrase. That is, X Agrees not with the specifier/adjunct but with the internal argument since X does not c-command the specifier/adjunct but only he internal argument, even under \citeposst{Kayne1994} definition of c-com\-mand. Thus, the specifier/adjunct cannot be genitive.

In \figref{bindtreePOSS} and \figref{bindtreeINS}, both the instrumental agents `Ivan.{\INS}' and the possessive adjective `Ivan's' do c-command the objects \textit{ego} `him' since the VoiceP$_1$ and VoiceP$_2$ are segments.
In other words, this structure correctly predicts the ungrammaticality of \REF{contPOSS}, but
it also incorrectly predicts \REF{contINS} to be ungrammatical. Thus, the contrast in \REF{binins} cannot be captured with \figref{bindtreePOSS} and \figref{bindtreeINS}. Something needs to be added to address the observed contrast in grammaticality.

I assume that instrumental agents are introduced as PP with a silent P head as in \figref{ins2}. With this extra layer of structure there is no Condition B violation since the PP blocks the instrumental agent's c-commanding the object.

\begin{figure}[h]
\caption{The modified version of the structure of \REF{contINS}}
\label{ins2}
\begin{forest}
  sn edges [ VoiceP$_1$ [ VoiceP$_2$ [ Voice [ violation ] ] 
                                     [ XP [ X ]
                                          [ \textit{n}P [ \textit{n} ] 
                                                      [ $\surd$P [ $\surd$ ] 
                                                                 [ rules.{\GEN} ] ] ] ] ] 
                        [ PP [ P [ φ ] ]
                                 [ Ivan.{\INS}$_i$ ] ] ]
\end{forest}
\end{figure}

\section{Generalized Case Realization Requirement}\label{sec:GCRR}

To capture the contrast in \REF{binins}--\REF{binins2}, I assumed that instrumental agents are introduces by the silent P.
However, it is undesirable to utilize an abstract element with no evidence.
Thus, I need some evidence except the contrasts in \REF{binins}--\REF{binins2}.
In this section, I demonstrate that assuming the silent P in instrumental agent phrases is a consequence of GCRR, proposed by \citet{Horvath2014}.


\subsection{Generalized Case Realization Requirement in Serbo-Croatian}


\citet{Horvath2014} addressed distribution of indeclinable nouns in Serbo-Croatian.
As shown in \REF{SCind}, 
the indeclinable name \textit{Miki} is ungrammatical although the declinable name \textit{Larisa} is grammatical in the oblique environment.

\begin{exe}
\ex\label{SCind} 
\begin{xlist}
\ex
\gll	Divim se \minsp{\{} Larisi / \minsp{*} Miki\}.\\
		admire.1{\SG} {\REFL} {} Larisa.{\DAT} {} {} Miki\\
\trans	`I admire Larisa/Miki.'
%\newpage
\ex
\gll	Ponosim se \minsp{\{} Larisom / \minsp{*} Miki\}.\\
		be.proud.1{\SG} {\REFL} {} Larisa.{\INS} {} {} Miki\\
\trans	`I am proud of Larisa/Miki.'
%\newpage
\ex
\gll	Oduševjena sam \minsp{\{} Larisom / \minsp{*} Miki\}.\\
		impressed.{\PTCP}.\textsc{f} {\AUX}.1{\SG} {} Larisa.{\INS} {} {} Miki\\\samepage
\trans	`I am impressed by Larisa/Miki.'
\hfill\citep[121]{Horvath2014}
\end{xlist}
\end{exe}

\noindent
The indeclinable name is grammatical with the declinable possessive \textit{moj} `my' or adjective \textit{lep} `beautiful', but it is ungrammatical without them or with the indeclinable adjective \textit{braon} `brown', as in \REF{SCmy}.


\begin{exe}
\ex\label{SCmy}  
\begin{xlist}
\ex
\gll	Divim se *(\hspace{-2pt} mojoj) Miki.\\
		admire.1{\SG} {\REFL} {} my.{\DAT.\SG} Miki\\
\trans	`I admire (my) Miki.'

\ex
\gll	Oduševjena sam *(\hspace{-2pt} mojom) Miki.\\
		impressed.{\SG}.\textsc{f} {\AUX}.1{\SG} {} my.{\INS}.{\SG} Miki\\
\trans	`I am impressed by (my) Miki.'

\ex
\gll	Divim se \minsp{\{*} braon / lepoj\} Miki.\\
		admire.1{\SG} {\REFL} {} brown {} beautiful.{\DAT}.{\SG} Miki\\
\trans	`I admire \{brunette/beautiful\} Miki.'
\hfill\citep[121]{Horvath2014}
\end{xlist}
\end{exe}

\noindent
In addition, the indeclinable name is grammatical with P even without the declinable possessive or adjective as illustrated in \REF{SCprep}.


\begin{exe}
\ex\label{SCprep}  
\begin{xlist}
\ex
\gll	On je trčao prema (\hspace{-2pt} lepoj) Miki.\\
		he {\AUX}.3{\SG} run.{\PTCP}.{\SG} towards {} beautiful.{\DAT.\SG} Miki\\
\trans	`He ran towards (beautiful) Miki.'

\ex
\gll	Dolazim sa (\hspace{-2pt} mojom) Miki.\\
		come.{1\SG} with {} my.{\INS} Miki\\
\trans	`I am coming with (my) Miki.'

\ex
\gll	Razgovarali smo o (\hspace{-2pt} mojoj) Miki.\\
		talk.{\PTCP.\PL} {\AUX.1\PL} about {} my.{\LOC} Miki\\
\trans	`I talked about (my) Miki.'
\hfill\citep[122-123]{Horvath2014}
\end{xlist}
\end{exe}

\noindent Accepting \citeposst{Pesetsky2013} theory of Case, \cite{Horvath2014} generalized these complicated phenomena of   Serbo-Croatian indeclinable nouns in the form of GCRR shown in \REF{GCRR}.


\begin{exe}\ex \textit{Generalized Case Realization Requirement (GCRR)} \label{GCRR}\\
Oblique cases must be overtly realized by some element of the 
\textsc{assignment domain} (where assignment domain consists of the assigning head and the assignee -- its noun phrase complement).
\hfill\citep[125]{Horvath2014}
\end{exe}

\noindent
According to GCRR, the sentences with the indeclinable name \textit{Miki} in \REF{SCind} are ungrammatical since no element in the assignment domain overtly realizes oblique cases.
As for \REF{SCmy}, sentences are grammatical even with the indeclinable name \textit{Miki} if the declinable possessive \textit{moj} `my' or adjective \textit{lep} `beautiful' overtly realizes oblique cases.
However it is ungrammatical without them or with the indeclinable adjective \textit{braon} `brown' because of the absence of overt realization of oblique cases.
In the case of \REF{SCprep}, each P \textit{prema} `towards,' \textit{sa} `with,' \textit{o} `about' manifests oblique cases and thus
 the sentences are grammatical even if there is no declinable possessive or adjective.


\subsection{Generalized Case Realization Requirement in Russian}

%There are some data supporting GCRR also in Russian.
There are also examples supporting the application of GCRR in Russian.\footnote{
            I consulted four Russian native speakers in their twenties for acceptability judgments on \REF{gcrrRR}. All speakers found \REF{gcrrRRb} unacceptable, but there was variation among speakers on \REF{gcrrRRa} and \REF{gcrrRRc}; three consider them acceptable (but unnatural) and the other considers them unacceptable. The speakers accepting \REF{gcrrRRa} also accept \REF{gcrrRRc} and \textit{vice versa}. What is important here is that some speakers accept \REF{gcrrRRa}, \REF{gcrrRRc} and that a clear difference in acceptability can be found between  \REF{gcrrRRa}/\REF{gcrrRRc} and \REF{gcrrRRb}.
            }

\begin{exe}
\ex \label{gcrrRR}%Supporting evidence for GCRR in Russian
%null P licensing the instrumental Case:
\begin{xlist}
\ex[?]{\label{gcrrRRa}
\gll Professor priexal v Moskvu s okolo pjati studentov.\\
	professor arrived to Moscow with about five.{\GEN} students.{\GEN}\\
\trans `Professor arrived at Moscow with about five students.'}
\ex[*]{\label{gcrrRRb}
%Covert P: * (neither P nor its Comp realizes {\INS})
\gll Professor rukovodit okolo pjati studentov.\\
	professor supervise about five.{\GEN} students.{\GEN}\\
\trans Intended: `Professor supervises about five students.'}
\ex[?]{\label{gcrrRRc}
\gll Professor rukovodit okolo pjat'ju studentami.\\
	professor supervise about five.{\INS} students.{\INS}\\
\trans `Professor supervises about five students.'}
\end{xlist}
\end{exe}

\noindent
Sentence \REF{gcrrRRa} is grammatical with P requiring the instrumental case \textit{s} `with'. In this case, there is an overt P and it realizes the instrumental case in the assignment domain.
However, \REF{gcrrRRb}, without manifestations of the instrumental case, is ungrammatical. This is because neither P nor its complement overtly realizes the instrumental case.
In addition, \REF{gcrrRRc} is grammatical since the complement \textit{pjat' studentov} `five students' is declined to bear the instrumental case, although the preposition \textit{okolo} `about' 
requires its complement in genitive Case.
The (un)grammaticality of these sentences are predicted by GCRR, which means that GCRR is valid not only in Serbo-Croatian but also in Russian.


\citet{Pesetsky2013} points out examples like \REF{gcrrRR}.
As shown in \REF{gcrrRRPese}, without manifestations of the instrumental case, the sentences show low acceptability and with P requiring the instrumental case or with an instrumental adjective, the sentences are grammatical.


\begin{exe}
\ex \label{gcrrRRPese}
\begin{xlist}
\ex[]{
\gll Ja čital \textit{Po kom zvonit kolokol}.\\
	I read \textit{For Whom the Bell Tolls}\\
\trans `I read \textit{For Whom the Bell Tolls}.'}
\ex[??]{
\gll Ja vosxiščajus' \textit{Po kom zvonit kolokol}. \\
	I admire \textit{For Whom the Bell Tolls}\\
\trans `I admire \textit{For Whom the Bell Tolls}.'}
\ex[?]{
\gll Ja vosxiščajus' zamečatel'nym \textit{Po kom zvonit kolokol}.\\
	I admire marvelous.{\INS} \textit{For Whom the Bell Tolls}\\
\trans `I admire the marvelous \textit{For Whom the Bell Tolls.}'}
%\newpage
\ex[]{
\gll Pomnju, kak diko rydala nad \textit{Po kom zvonit kolokol}.\\
	remember.1 how wildly cried.{\SG}.\textsc{f} over \textit{For Whom the Bell Tolls}\\
\trans `I remember how wildly I cried over \textit{For Whom the Bell Tolls.}'}
\end{xlist}\hfill\citep[132]{Pesetsky2013}
\end{exe}

\noindent
In addition, if GCRR is active, it is predicted that \REF{ivan} becomes ungrammatical when the declinable name \textit{Ivan} is replaced with an indeclinable name, as in that case there is no manifestation of the instrumental case. 
This is confirmed in \REF{shmit}, where the indeclinable name \textit{Šmidt} is used.

\begin{exe}
\ex\label{insIVSH}
\begin{xlist}
\ex[]{\label{ivan}
\gll  Narušenie  {pravil}  {Ivanom}$_i$  ogorčaet  ego$_i$.\\
	violation rule.{\GEN} Ivan.{\INS} distresses him\\
\trans `The violation of the rules by Ivan$_i$ distresses him$_i$.'}
\ex[*]{\label{shmit}
\gll  Narušenie  {pravil}  {Šmidt}$_i$  ogorčaet  ego$_i$.\\
	 violation rule.{\GEN} Schmidt distresses him\\
\trans Intended: `The violation of the rules by Schmidt$_i$ distresses him$_i$.'}
\end{xlist}
\end{exe}

\noindent
Thus there are reasons to assume the existance of a silent P, which introduces instrumental agent as proposed in \figref{ins2} since GCRR is (at least roughly) valid in Russian as mentioned above. 
%In other words, there is no problem with assuming the existence of the silent P introducing instrumental agents since complements of P realizes the instrumental case as GCRR indicates. 


\section{Binding out of PP}\label{sec:PP}

\subsection{Functional and lexical prepositions}

\citet{YadroffFranks2001} proposed a distinction between \textsc{functional prepositions} (functinal P) such as \textit{u} `at', \textit{k} `toward',  \textit{bez} `without' and \textsc{lexical prepositions} (lexical P) such as \textit{okolo} `around', \textit{blagodarja} `thanks to', \textit{otnositel'no} `with respect to' in various grammatical respects as illustrated in  \tabref{FCP}. 

%\newpage
\begin{table}[h]
  \centering
  \caption{Functional and lexical prepositions \citep[70]{YadroffFranks2001}}
    \begin{tabularx}{\textwidth}{p{1em}p{13em}p{1em}p{13em}}\lsptoprule
    \multicolumn{2}{p{15em}}{Functional prepositions } & \multicolumn{2}{p{15em}}{Lexical prepositions} \\\midrule\addlinespace
    \multicolumn{2}{p{14em}}{\textit{Phonology}} & \multicolumn{1}{r}{} & \multicolumn{1}{r}{} \\
    A.    & Unstressed  & A.    & Stressed \\
    B.    & Monosyllabic & B.    & Polysyllabic \\\addlinespace
    \multicolumn{2}{p{14em}}{\textit{Morphology}} & \multicolumn{1}{r}{} & \multicolumn{1}{r}{} \\
    C.    & Monomorphemic & C.    & Often polymorphemic or compound \\
    D.    & Prothetic \textit{n}- before 3rd-person pronouns & D.    & No prothetic \textit{n}- \\\addlinespace
    \multicolumn{2}{p{14em}}{\textit{Syntax}} & \multicolumn{1}{r}{} & \multicolumn{1}{r}{} \\
    E.    & Object is obligatory & E.    & Object may be optional \\
    F.    & Approximative inversion yields N before P  & F.    & Approximative inversion yields P before N \\
    G.    & Negative particle \textit{ni} does not intervene & G.    & \textit{Ni} intervenes \\
    H.    & May be doubled in colloquial language & H.    & Cannot be doubled \\
    I.    & May be lexically selected & I.    & Cannot be lexically selected \\
    J.    & Allow binding out of PP & J.    & Block binding out of PP \\
    K.    & No intercalating particles & K.    & Intercalating particles \\
    L.    & May govern multiple cases & L.    & Govern one specific case \\\addlinespace
    \multicolumn{2}{p{14em}}{\textit{Semantics}} & \multicolumn{1}{r}{} & \multicolumn{1}{r}{} \\
    M.    & Meaning abstract (hence polysemous) & M.    & Meaning concrete (therefore fixed) \\\lspbottomrule
    \end{tabularx}
  \label{FCP}
\end{table}
%\vspace{-.8em}
%\hfill\citep[70]{YadroffFranks2001}
%\vspace{1em}

To capture the various differences between functional P and lexical P, 
\citet{YadroffFranks2001} assume two different syntactic structures for  each type of P.  \figref{trFP} and \figref{trLP} give their structure of the two PPs in \REF{PP}. 

\begin{multicols}{2}
\begin{exe}\ex \label{PP}
\begin{xlist}
\ex\label{Pk}
\gll  k ženščinam\\
	towards women.{\DAT}\\
\trans `towards women'
\ex\label{Pb}
\gll  blagodarja ženščinam\\
	thanks.to women.{\DAT}\\\samepage
\trans `thanks to women'
\end{xlist}
\end{exe}
\end{multicols}

\begin{figure}[h]
\caption{The structure of \REF{Pk} \citep[77]{YadroffFranks2001}}
%PP with functional P \textit{k} \citep[77]{YadroffFranks2001}}
\label{trFP}
%\Tree [.FP [.F k\\{[Target]}\\{[Dative]} ] \qroof{ženščinam}.NP ]
\begin{forest}
  sn edges [ FP [ F [ {towards\\\relax[Target\relax]\\\relax[Dative\relax]} ] ]
                [ NP [ women.{\DAT}, roof] ] ]
\end{forest}
\end{figure}

\begin{figure}[h]
\caption{The structure of \REF{Pb} \citep[78]{YadroffFranks2001}}
%PP with lexical P \textit{blagodarja} \citep[78]{YadroffFranks2001}}
\label{trLP}
%\Tree [.XP [.X blagodarja\\{[Complex θ-role]} ] [.FP [.F ø\\{[Beneficiary]}\\{[Dative]}\\{[+def]} ]!\qsetw{0.6in} \qroof{ženščinam}.NP ]!\qsetw{1in} ]
\begin{forest}
  sn edges [ XP [ X [ {thanks.to\\\relax[Complex θ-role\relax]} ] ]
                [ FP [ F [ {ø\\\relax[Beneficiary\relax]\\\relax[Dative\relax]\\\relax[+def\relax]} ] ]
                     [ NP [ women.{\DAT}, roof] ] ] ]
\end{forest}
\end{figure}

\noindent
``X'' is used to indicate that here, \textit{blagodarja} `thanks to' is a bleached lexical item, which lacks a functional structure.\footnote{
			Please see \citet{YadroffFranks2001} for more detail.
			}


\subsection{Binding possibility out of lexical PP}

I showed that a silent P is required to capture the contrasts in \REF{binins}--\REF{binins2}  
and that assuming a silent P is valid as shown in the data regarding GCRR in Russian in \sectref{sec:GCRR}.

However, binding out of PP is not necessarily blocked as, for example, \citet{YadroffFranks2001, Bailyn2010} point out.
With regard to binding possibility (J in \tabref{FCP}), a functional P allows binding out of PP as shown in \REF{ppbinda} and a lexical P blocks binding out of PP as in \REF{ppbindb}.\footnote{
			\citet{YadroffFranks2001} point out that there is also a similar contrast in English.
			\ea
            \ea[]{John spoke to [Bill and Mary]$_i$ about each other$_i$'s birthdays.}
			\ex[*]{John spoke about [Bill and Mary]$_i$ in each other$_i$'s houses.}
\hfill \citep[74]{YadroffFranks2001}
			\z\z
			
			\noindent
			\citet{Bailyn2010} also points out data similar to \REF{ppbind}.
			Binding out of PP \textit{u Petrovyx} `at the Petrovs' is allowed.			
			
			\ea\label{ppbind2}
			\gll	U Petrovyx$_i$ byla svoja$_i$ komnata.\\
					at the.Petrovs was self's.{\NOM} room.{\NOM}\\
			\glt `The Petrovs had their own room.'
			\hfill\citep[14]{Bailyn2010}
			\z}

\begin{exe}\ex \label{ppbind}
\begin{xlist}
\ex \label{ppbinda}
\gll	U ėtogo čeloveka$_i$ vsegda est' svoi$_i$ original'nye idei.\\
		at this person always be self's original idea\\\samepage
\trans `In that person's head there are always his own original ideas.'

\ex\label{ppbindb}	
\gll	* Okolo ėtogo čeloveka$_i$ vsegda est' svoi$_i$ original'nye idei.\\
		{} around this person always be self's original idea\\
\trans Intended: `Around that person there are always his own original ideas.'
\end{xlist}\samepage\hfill\citep[74]{YadroffFranks2001}
\end{exe}

\noindent Given the grammaticality of \REF{ppbinda}, the silent P (ø) is a lexical P.
Therefore, the structure of \REF{contINS}, shown in \figref{ins2}, should be modified to \figref{trinsXP}.\footnote{
			There are two X(P) in this tree. 
			However, note that it is not guaranteed that they are the same projection.
			``X'' whose sister is \textit{n}P represents a genitive assigner as described in 
			\citet{MiyauchiIto2016, Miyauchi2017b}. 
			``X'' whose sister is FP is used to indicate that the silent P is a bleached lexical item \citep{YadroffFranks2001}.
			}

\begin{figure}[h]
\caption{The structure of \REF{contINS}}
\label{trinsXP}
\begin{forest}
  sn edges [ VoiceP$_1$ [ VoiceP$_2$ [ Voice [ violation ] ] 
                                     [ XP [ X ]
                                          [ \textit{n}P [ \textit{n} ] 
                                                      [ $\surd$P [ $\surd$ ] 
                                                                 [ rules.{\GEN} ] ] ] ] ] 
                        [ XP [ X [ ø ] ]
                             [ FP [ F [ ø ] ]
                                  [ Ivan.{\INS}$_i$ ] ] ] ]
\end{forest}
\end{figure}


\section{Conclusion}\label{sec:CON}

In this paper, I have argued that instrumental agents in Russian are introduced by a silent (lexical) P. As I have shown, this PP layer blocks binding of instrumental agents outside the event nominal, which is otherwise possible for agents introduced as possessors. My analysis which assumes Russian event nominals (or noun phrases more generally) lack the DP layer also offers (at least partial) support to the idea that GCRR is active in Russian.



\section*{Abbreviations}

\begin{tabularx}{.5\textwidth}{lX}
1 & first person \\ 
3 & third person\\
\textsc{acc} & accusative \\ 
\textsc{Ag} & agent (θ-role) \\ 
\textsc{aux} & auxiliary \\ 
CEN & complex event nominals \\
\textsc{dat} & dative \\ 
\textsc{f} & feminine \\ 
GCRR & generalized case \\
 &realization requirement \\
\textsc{gen} & genitive  \\ 
\end{tabularx}
\begin{tabularx}{.45\textwidth}{lX}
\textsc{inf} & infinitive \\ 
\textsc{int-arg} & internal argument \\ 
\textsc{ins} & instrumental \\ 
\textsc{loc} & locative  \\ 
PIC & phase impenetrability\\
&condition \\
\textsc{pl} & plural \\ 
\textsc{Poss} & possessor (θ-role) \\ 
\textsc{ptcp} & participle \\ 
\textsc{refl}&reflexive \\ 
\textsc{sg} & singular \\ 
\end{tabularx}



\section*{Acknowledgements}
	I am grateful to the FDSL 12.5 participants for their valuable suggestions. In addition, I would like to thank anonymous reviewers for insightful comments. I also appreciate my informants reviewing the Russian data. The research reported here was supported by JSPS Grants-in-Aid for Scientific Research (\#17J07534, \#19K23073, PI: Takuya Miyauchi). All misunderstandings and errors remain my own.
		
\sloppy
\printbibliography[heading=subbibliography,notkeyword=this]

\end{document}
